---
title: "Barrier Checks 2"
output: html_notebook
---

# Dependencies 

This notebooke requires the following packages:

```{r, message=FALSE, warning=FALSE}
library(dplyr)
library(rgdal)
library(broom)
```

# Import Data

The raw data come from two tables (location data for each barrier and google maps verification data for each barrier) as well as a shapefile of all barriers we've geocoded to date:

```{r, warning=FALSE}
# import tabular data
allBarriers  <- read.csv("allBarriers.csv", stringsAsFactors = FALSE)

# change working directory for remainder of code chunk (will reset at end of chunk)
setwd('..')
setwd("spatialData")

# import spatial data
barrierGeo    <- readOGR(dsn = ".", layer = "MergedShapefile")

# convert spatial data to data frame
barrierGeo    <- tidy(barrierGeo)
```

# Combine Data Sources

To faciliate the join below, we need to rename the identification barrier in `barrierGeo` from `BarrierID` to `id`:

```{r}
barrierGeo <- rename(barrierGeo, id = BarrierID)
```

We also re-sort the barriers in both data frames so that they are both in ascending numerical order:

```{r}
barrierGeo <-  arrange(barrierGeo, id) 
allBarriers <-  arrange(allBarriers, id)
```

In order to check these data to identify barriers that we have not yet geocoded, all of the raw data are joined together:

```{r}
barrierChecks2 <- left_join(allBarriers, barrierGeo, by = "id")
```

# Simplify Barrier Status & Test to Confirm That All Street Closed Barriers Have Been Geocoded

```{r}
barrierChecks2$test1 <- ifelse(barrierChecks2$status == "street closed", TRUE, FALSE)

barrierPass2 <- barrierChecks2 %>%
  filter(test1 == TRUE)

barrierPass2$test2 <- ifelse(is.na(barrierPass2$coords.x1) == TRUE, "fail", "pass")

# barrierFail2 <- barrierChecks2 %>%
#  filter(test1 == FALSE)
```

```{r}
allBarriers <- barrierChecks2 %>%
  select(id, status)
write.csv(allBarriers, "allBarriers_v2.csv")
```

